Correlation Clustering with Dynamic Super-Nodes (DySNCC)

### 2014-10-09 paper/egpaper_for_review.tex
improved paper

>>>>

\subsubsection{Randomized HierarchicalClustering (RHC)}

To generate proposals cut we can use bottom up hierarchical clustering.
In each step we contract the edge with the highest weight.
Parallel edges are merged into single edges by summing their weights.
We stop when a certain number of nodes is reached, or the
largest edge weight is smaller then a certain threshold.
To get versatile proposals we either add noise 
to the edge weighs or permute a certain number of weights.

\subsubsection{Randomized MaxCut  (RMC)}

To get energy aware proposals we can use max cuts.
The max cut objective is the same as
the multicut objective, but only two 
node colors are allowed.
Therefore solutions of the max cut objective
might be useful proposals.
To create different proposals we set 
the weight of edges which are cut 
in the best solution to zero.
In this way we favor solutions 
different form the current best. 
In addition we either add noise permute a certain number of weights.

\subsubsection{Randomized Watersheds (RWS)}

The edge weighted watershed algorithm
with random seeds can be used to get 
cheap proposals.
